Medical Concept Extraction

### 2012-12-17 paper/paper.tex
table fix
Adding confusion matrix figure.

@@

\begin{figure}
\begin{center}
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l||l|l|}
	\hline
	\multicolumn{11}{|c||}{\bf Feature Set} & \multicolumn{2}{|c|}{\bf F1 Score}	\\ \hline
	% BEGIN COLUMN HEADERS
		\begin{sideways} length \end{sideways} & 
		\begin{sideways} mitre \end{sideways} & 
		\begin{sideways} next \end{sideways} & 
		\begin{sideways} pos \end{sideways} & 
		\begin{sideways} prev \end{sideways} & 
		\begin{sideways} stem\_lancaster \end{sideways} & 
		\begin{sideways} stem\_porter \end{sideways} & 
		\begin{sideways} stem\_wordnet \end{sideways} & 
		\begin{sideways} test\_result \end{sideways} & 
		\begin{sideways} word \end{sideways} & 
		\begin{sideways} word\_shape \end{sideways} & 
		LIN & CRF	\\ \hline
	% END COLUMN HEAERS

	\checkmark & & & & & & & & & & & 0.2157 & 0.0420	\\ \hline
	& \checkmark & & & & & & & & & & 0.2155 & 0.0927	\\ \hline
	& & \checkmark & & & & & & & & & 0.2155 & 0.0572	\\ \hline
	& & & \checkmark & & & & & & & & 0.2155 & 0.0820	\\ \hline
	& & & & \checkmark & & & & & & & 0.2155 & 0.0366	\\ \hline
	& & & & & \checkmark & & & & & & 0.7085 & 0.2878	\\ \hline
	& & & & & & \checkmark & & & & & 0.7266 & 0.2886	\\ \hline
	& & & & & & & \checkmark & & & & 0.7309 & 0.2857	\\ \hline
	& & & & & & & & \checkmark & & & 0.2806 & 0.1084	\\ \hline
	& & & & & & & & & \checkmark & & 0.7332 & 0.2753	\\ \hline
	& & & & & & & & & & \checkmark & 0.2431 & 0.1244	\\ \hline

\end{tabular}
\end{center}
\caption{A summary of the F1-scores from many different models with different features enabled.}
\label{fig:summary_f1_scores}
\end{figure}

Overall we found that our system did a good job at predicting labels for medical notes. Figure~\ref{fig:all_features_results} shows summary statistics as well as a confusion matrix of a model that was trained with all the features enabled. The results are broken down so we can see the relative performance of each of the individual classifiers. Overall, the system does very well and achieves an average F1-score of {\bf 0.79}.

>>>>

\begin{figure}[t]
\begin{center}
	\begin{tabular}{|l|l|l|l|l|}
	\hline
	\multicolumn{5}{|c|}{\bf crfsuite} \\ \hline
	& test & problem & none & treatment \\ \hline
	test & 14388 & 1503 & 932 & 414	\\ \hline
	problem & 288 & 27993 & 1521 & 474	\\ \hline
	none & 3214 & 18463 & 175032 & 5729	\\ \hline
	treatment & 304 & 1896 & 1418 & 13680	\\ \hline

	\end{tabular}
\end{center}

\begin{center}
	\begin{tabular}{|l|l|l|l|l|}
	\hline
	\multicolumn{5}{|c|}{\bf liblinear} \\ \hline
	& test & problem & none & treatment \\ \hline
	test & 11819 & 1171 & 3718 & 529	\\ \hline
	problem & 475 & 22682 & 6383 & 736	\\ \hline
	none & 1120 & 4408 & 195085 & 1825	\\ \hline
	treatment & 249 & 1251 & 4099 & 11699	\\ \hline

	\end{tabular}
\end{center}

\begin{center}
	\begin{tabular}{|l|l|l|l|l|}
	\hline
	\multicolumn{5}{|c|}{\bf libsvm} \\ \hline
	& test & problem & none & treatment \\ \hline
	test & 12741 & 1179 & 2935 & 382	\\ \hline
	problem & 542 & 23288 & 5818 & 628	\\ \hline
	none & 1284 & 4175 & 195716 & 1263	\\ \hline
	treatment & 438 & 1989 & 3860 & 11011	\\ \hline

	\end{tabular}
\end{center}

\caption{Confusion matrix for a model trained on all of the test data with all of the features enabled.}
\label{fig:all_confusion_matrix}
\end{figure}

@@

\begin{figure*}[ht]
\begin{center}
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l||l|l|}
	\hline
	\multicolumn{11}{|c||}{\bf Feature Set} & \multicolumn{2}{|c|}{\bf F1 Score}	\\ \hline
	% BEGIN COLUMN HEADERS
		\begin{sideways} length \end{sideways} & 
		\begin{sideways} mitre \end{sideways} & 
		\begin{sideways} next \end{sideways} & 
		\begin{sideways} pos \end{sideways} & 
		\begin{sideways} prev \end{sideways} & 
		\begin{sideways} stem\_lancaster \end{sideways} & 
		\begin{sideways} stem\_porter \end{sideways} & 
		\begin{sideways} stem\_wordnet \end{sideways} & 
		\begin{sideways} test\_result \end{sideways} & 
		\begin{sideways} word \end{sideways} & 
		\begin{sideways} word\_shape \end{sideways} & 
		LIN & CRF	\\ \hline
	% END COLUMN HEAERS

	\checkmark & & & & & & & & & & & 0.2157 & 0.0420	\\ \hline
	& \checkmark & & & & & & & & & & 0.2155 & 0.0927	\\ \hline
	& & \checkmark & & & & & & & & & 0.2155 & 0.0572	\\ \hline
	& & & \checkmark & & & & & & & & 0.2155 & 0.0820	\\ \hline
	& & & & \checkmark & & & & & & & 0.2155 & 0.0366	\\ \hline
	& & & & & \checkmark & & & & & & 0.7085 & 0.2878	\\ \hline
	& & & & & & \checkmark & & & & & 0.7266 & 0.2886	\\ \hline
	& & & & & & & \checkmark & & & & 0.7309 & 0.2857	\\ \hline
	& & & & & & & & \checkmark & & & 0.2806 & 0.1084	\\ \hline
	& & & & & & & & & \checkmark & & 0.7332 & 0.2753	\\ \hline
	& & & & & & & & & & \checkmark & 0.2431 & 0.1244	\\ \hline
	\checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & 0.8001 & 0.7891	\\ \hline

\end{tabular}
\end{center}
\caption{A summary of the F1-scores from many different models with different features enabled.}
\label{fig:summary_f1_scores}
\end{figure*}

Overall we found that our system did a good job at predicting labels for medical notes. Figure~\ref{fig:all_confusion_matrix} shows a confusion matrix of a model that was trained with all features enabled and Figure~\ref{fig:all_features_results} shows summary statistics for that very same model. The results are broken down so we can see the relative performance of each of the individual classifiers. Overall, the system does very well and achieves an average F1-score of {\bf 0.79}.
